---
title: "Board Meeting Slides"
author: "Karl Polen"
date: "May 14, 2020"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

```{r}
library(tidyr)
library(ggplot2)
library(stringr)
pe_multiplier=seq(15,30,1)
eps2750=2750/pe_multiplier
eps2500=2500/pe_multiplier
eps2250=2250/pe_multiplier
eps2000=2000/pe_multiplier
eps3000=3000/pe_multiplier
eps3250=3250/pe_multiplier
eps3500=3500/pe_multiplier
cm=data.frame(pe_multiplier,eps2000,eps2250,eps2500,eps2750,eps3000,eps3250,eps3500)
cmlong=gather(cm,"iso","Earnings_per_share",-pe_multiplier)
cmlong$iso=str_sub(cmlong$iso,4)
ggplot(cmlong,aes(y=Earnings_per_share,x=pe_multiplier,group=iso,color=iso))+geom_line()
```
